A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-11-06 CWP/papers/HSF-CWP-2017-01_roadmap/latex/cwp-main.tex
Add comment about GPUs to ML section

With the advent of more powerful hardware and more performant ML
algorithms, the ML toolset will be used to develop application software
that could potentially, amongst other things:

>>>>

With the advent of more powerful hardware, particularly GPUs and ML dedicated
processors, as well as more performant ML
algorithms, the ML toolset will be used to develop application software
that could potentially, amongst other things:
